### 2021-04-20 paper/maxdet.tex
Added the uniqueness result.

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}{Definition}
\newenvironment{proof}[1][Proof]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}

@@

\subsection{Zeroes \& the inverse matrix}
A remarkable formula due to Babachiewicz \cite{horn} expresses the inverse of a matrix in terms of the Schur complement. For a matrix
\begin{equation}\label{eqn.sigma}
	\Sigma = \begin{pmatrix}
		\Sigma_{11} & \Sigma_{12} \\ 
		\Sigma_{21} & \Sigma_{22}
	\end{pmatrix}
\end{equation}
we have
\begin{equation}
	\Sigma^{-1} = \begin{pmatrix}
		\Sigma_{11}^{-1} + \Sigma_{11}^{-1}\Sigma_{12}(\Sigma/\Sigma_{11})^{-1}\Sigma_{21}\Sigma_{11}^{-1} &-\Sigma_{11}^{-1} \Sigma_{12} (\Sigma/\Sigma_{11})^{-1} \\ 
		-(\Sigma/\Sigma_{11})^{-1}\Sigma_{21}\Sigma_{11}^{-1} & (\Sigma/\Sigma_{11})^{-1}
	\end{pmatrix}.
\end{equation}
This formula has the remarkable property that only the inverses 
\begin{equation}
	\Sigma_{11}^{-1} \text{\ and\ } (\Sigma/\Sigma_{11})^{-1}
\end{equation}
appear in it. With our choice of $W$ in equation (\ref{eqn.choice}) the Schur complement $M/E$ is block diagonal. This means that also its inverse is block diagonal. Indeed, we have
\begin{equation}
	(M/E)^{-1} = \begin{pmatrix}
		(M[\alpha]/E)^{-1} & 0 \\
		0 & (M[\beta]/E)^{-1}
	\end{pmatrix}.
\end{equation}
This allows us to write the inverse of $M$ explicitly:
\begin{equation}
	M^{-1} = \begin{pmatrix}
		(M[\alpha]/E)^{-1} & -(M[\alpha]/E)^{-1} D E^{-1} & 0 \\
		- E^{-1} D^T (M[\alpha]/E)^{-1} & \Xi & - E^{-1} F (M[\beta]/E)^{-1} \\
		0 & - (M[\beta]/E)^{-1} F^T E^{-1} & (M[\beta]/E)^{-1}
	\end{pmatrix},
\end{equation}
with
\begin{equation}
	\Xi = E^{-1} + E^{-1}\left(D^T(M[\alpha]/E)^{-1}D + F (M[\beta]/E)^{-1} F^T\right)E^{-1}.
\end{equation}
We see that the inverse of $M$ has zeroes in exactly those places where the undetermined matrix $W$ used to be.

@@

In the following we no longer assume that the matrices are non-singular. It turns out that we can still define the Schur complement of a matrix. For a matrix $E$ we will denote by $E^-$ a generalized inverse of $E$. $E^-$ is a matrix that satisfies
\begin{equation}
	E E^{-}E = E.
\end{equation}
A particular example of a generalized inverse is the Moore-Penrose inverse $E^+$ \cite{roger}. For now, we will not assume that we are dealing with $E^+$ but keep the discussion general. Given a particular choice of generalized inverse we define
\begin{equation}
	\Sigma/\Sigma_{11} = \Sigma_{22} - \Sigma_{21}\Sigma_{11}^-\Sigma_{12}.
\end{equation}
If $\Sigma$ is a symmetric matrix that is also positive semi-definite it turns out that the Schur complement does not depend on the choice of the particular generalized inverse used in its definition.

@@

\begin{theorem}
	Let $M$ be as in equation (\ref{eqn.corrmatrix}). Let both $M[\alpha]$ and $M[\beta]$ be positive semidefinite. Setting 
	\begin{align}
		W & = DE^-F \\
		  & = M[ \alpha-\gamma, \gamma]M[\gamma]^-M[ \gamma, \beta-\gamma]		
	\end{align}
	turns $M$ into a positive semidefinite matrix.
\end{theorem}

@@

>>>>

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}{Definition}
\newenvironment{proof}[1][Proof]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}

@@

\subsection{Zeroes \& the inverse matrix}
A remarkable formula due to Babachiewicz \cite{horn} expresses the inverse of a matrix in terms of the Schur complement. For a matrix
\begin{equation}\label{eqn.sigma}
	\Sigma = \begin{pmatrix}
		\Sigma_{11} & \Sigma_{12} \\ 
		\Sigma_{21} & \Sigma_{22}
	\end{pmatrix}
\end{equation}
we have
\begin{equation}\label{eqn.baba}
	\Sigma^{-1} = \begin{pmatrix}
		\Sigma_{11}^{-1} + \Sigma_{11}^{-1}\Sigma_{12}(\Sigma/\Sigma_{11})^{-1}\Sigma_{21}\Sigma_{11}^{-1} &-\Sigma_{11}^{-1} \Sigma_{12} (\Sigma/\Sigma_{11})^{-1} \\ 
		-(\Sigma/\Sigma_{11})^{-1}\Sigma_{21}\Sigma_{11}^{-1} & (\Sigma/\Sigma_{11})^{-1}
	\end{pmatrix}.
\end{equation}
This formula has the remarkable property that only the inverses 
\begin{equation}
	\Sigma_{11}^{-1} \text{\ and\ } (\Sigma/\Sigma_{11})^{-1}
\end{equation}
appear in it. With our choice of $W$ in equation (\ref{eqn.choice}) the Schur complement $M/E$ is block diagonal. This means that also its inverse is block diagonal. Indeed, we have
\begin{equation}
	(M/E)^{-1} = \begin{pmatrix}
		(M[\alpha]/E)^{-1} & 0 \\
		0 & (M[\beta]/E)^{-1}
	\end{pmatrix}.
\end{equation}
This allows us to write the inverse of $M$ explicitly:
\begin{equation}
	M^{-1} = \begin{pmatrix}
		(M[\alpha]/E)^{-1} & -(M[\alpha]/E)^{-1} D E^{-1} & 0 \\
		- E^{-1} D^T (M[\alpha]/E)^{-1} & \Xi & - E^{-1} F (M[\beta]/E)^{-1} \\
		0 & - (M[\beta]/E)^{-1} F^T E^{-1} & (M[\beta]/E)^{-1}
	\end{pmatrix},
\end{equation}
with
\begin{equation}
	\Xi = E^{-1} + E^{-1}\left(D^T(M[\alpha]/E)^{-1}D + F (M[\beta]/E)^{-1} F^T\right)E^{-1}.
\end{equation}
We see that the inverse of $M$ has zeroes in exactly those places where the undetermined matrix $W$ used to be.

@@

In the following we no longer assume that the matrices are non-singular. It turns out that we can still define the Schur complement of a matrix. For a matrix $E$ we will denote by $E^-$ a generalized inverse of $E$. $E^-$ is a matrix that satisfies
\begin{equation}
	E E^{-}E = E.
\end{equation}
A particular example of a generalized inverse is the Moore-Penrose inverse $E^+$ \cite{roger}. For now, we will not assume that we are dealing with $E^+$ but keep the discussion general. Let us look at a general matrix $\Sigma$ as in equation (\ref{eqn.sigma}). Given a particular choice of generalized inverse we define
\begin{equation}
	\Sigma/\Sigma_{11} = \Sigma_{22} - \Sigma_{21}\Sigma_{11}^-\Sigma_{12}.
\end{equation}
If $\Sigma$ is a symmetric matrix that is also positive semi-definite it turns out that the Schur complement does not depend on the choice of the particular generalized inverse used in its definition.

@@

\begin{theorem}
	Let $M$ be as in equation (\ref{eqn.corrmatrix}). Let both $M[\alpha]$ and $M[\beta]$ be positive semidefinite. Let $E^-$ be a generalized inverse of $E$ that is also symmetric. Setting 
	\begin{align}
		W & = DE^-F \\
		  & = M[ \alpha-\gamma, \gamma]M[\gamma]^-M[ \gamma, \beta-\gamma]		
	\end{align}
	turns $M$ into a positive semidefinite matrix.
\end{theorem}

@@

We next look at the generalized inverse $M^+$ of $M$. It turns out that it can be uniquely expressed in terms of the Schur complement. This is a generalization of the Babachiewicz's result from equation (\ref{eqn.baba}) to the semidefinite case.

\begin{theorem}
	Let $\Sigma$ be a symmetric matrix partitioned as in equation (\ref{eqn.sigma}). Then we have
	\begin{equation}
		\Sigma^+ = \begin{pmatrix}\label{eqn.mpinverse}
		\Sigma_{11}^{+} + \Sigma_{11}^{+}\Sigma_{12}(\Sigma/\Sigma_{11})^{+}\Sigma_{21}\Sigma_{11}^{+} &-\Sigma_{11}^{+} \Sigma_{12} (\Sigma/\Sigma_{11})^{+} \\ 
		-(\Sigma/\Sigma_{11})^{+}\Sigma_{21}\Sigma_{11}^{+} & (\Sigma/\Sigma_{11})^{+}
	\end{pmatrix}
	\end{equation}
	if and only if 
	\begin{equation}\label{eqn.rank}
			r(\Sigma) = r(\Sigma_{11}) + r(\Sigma_{22}).		
	\end{equation}
\end{theorem}

\begin{proof}
	See \cite[section 4]{ouellette} and \cite{horn}. \qed
\end{proof}

For a symmetric positive semidefinite matrix $\Sigma$ the condition on the rank of $\Sigma$ is automatically satisfied. We thus have the following corollary:

\begin{corollary}\label{cor.inverse}
	Let $\Sigma$ be symmetric and positive semidefinite. Then $\Sigma^+$ is given by equation (\ref{eqn.mpinverse}).
\end{corollary}

We can now state a unique property of our completion:

\begin{theorem}
	The completion defined by setting $W=DE^+F$ is the unique completion that turns $M$ into a symmetric positive semidefinite matrix and for which $M^+$ has zeroes in the places where $W$ used to be.
\end{theorem}

The uniqueness result stated in \cite{smith} gives this result only for the positive definite case. This result shows that it is indeed also true for the positive semidefinite case.

\begin{proof}
	Because of the previous corollary \ref{cor.inverse} we see that for any completion $W$ that turns $M$ into a symmetric positive semidefinite matrix the Moore-Penrose inverse is given by equation (\ref{eqn.mpinverse}). This inverse has zeroes in exactly the places where $W$ used to be if and only if $W=DE^+F$. \qed	  
\end{proof}
